---
title: "A (very) short introduction to R"
author: "kaylavie"
output:
  pdf_document: default
  html_document: default
---

In this document you'll find a short introduction to the R programming language as described in https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf. The code and its output were generated with Rstudio, "R markdown"" and "knitr". 

**1. ToDo 3.1**
```{r}
abs((2016-2014)/(2014-1901)*100)
```
**2. ToDo 3.2**
```{r}
yob = 1901
start = 2016
life = 2014 - yob
school = 2014 - 2016
abs(school/life) * 100
```
**3. ToDo 3.3**
```{r}
vec=c(4,5,8,11)
sum(vec)
```
**4. ToDo 3.4**
```{r}
x=rnorm(100)
plot(x)
```
**5. ToDo 4**
```{r}
help(sqrt)
```

```{r,eval=FALSE}
f <- function(x) {
  # code would go here...
}
```
**6. ToDo 5**  

File > New File > RScript > Save > firstscript.R

```{r}
w=rnorm(100)
plot(w)
```

Run the script several times:  

 > source("firstscript.R")  
 > source("firstscript.R")  
 > source("firstscript.R")  
 > source("firstscript.R")   

Each run produces a different graph.
```{r}

```
**7. ToDo 6.2**
```{r}
P = seq(from=31, to = 60, by = 1)
Q = matrix(data=P, ncol=5, nrow=6)
```
**8. ToDo 6.3**  
File > New File > RScript > Save > dataframe.R 
```{r}
x1 = c(rnorm(100))  
x2 = c(rnorm(100))
x3 = c(rnorm(100))

t = data.frame(a=x1, b=x1+x2, c= x1+x2+x3)
plot(t)
sd(as.numeric(as.matrix(t)))
```

Run the script several times:  

 > source("dataframe.R")  
 > source("dataframe.R")  
 > source("dataframe.R")  
 > source("dataframe.R") 
 
Each run produces a different graph.  
```{r}

```
**9. ToDo 7**  
* append the following to dataframe.R
```{r}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2, col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,col=rgb(0,0,1,0.3))

```
**10. ToDo 8**
    
File > New File > Text File > Save > kay.txt  
a g x  
1 2 3  
2 4 6  
4 8 12  
8 16 24  
32 64 96  
```{r,echo=FALSE}

```
File > New File > RScript > Save > readfile.R  

 > var1 = read.table(file="kay.txt",  > header=TRUE)  
 > g = as.matrix(var1[,2])*5  
 > write.table(g, file="kay2.txt")  
```{r}

```
**11. ToDo 9**
```{r}
mean(sqrt(rnorm(100)))
```
**12. ToDo 10.2**
```{r}
presents = c(8, 16, 12)
date = strptime(c("20180224203000", "20181224000000", "20180830000000"), format="%Y%m%d%H%M%S")
plot(date, presents)
```
**13. ToDo 11.2**
```{r}
vect = seq(from=1, to=100)
s = c()
for (i in 1:length(vect))
{
  if (vect[i] <= 5)
  {
     s[i] = vect[i] * 10
  }
  else if (vect[i] >= 90)
  {
    s[i] = vect[i] * 10
  }
  else
  {
    s[i] = vect[i] * 0.1
  }
}
s
```
**14. ToDo 11.3**
```{r}
funckay = function(vect)
{
     s = c()
    for (i in 1:length(vect))
    {
        if (vect[i] <= 5)
        {
            s[i] = vect[i] * 10
        }
        else if (vect[i] >= 90)
        {
            s[i] = vect[i] * 10
        }
        else
        {
            s[i] = vect[i] * 0.1
        }
    }
    return (s) 
}
```

```{r}
funckay(vect)
```
**15. One More Thing ToDo**  
```{r}
c(vect[1:5]*10,vect[6:89]*0.1,vect[90:100]*10)
```
